### 2025-03-06 tutorials/getstarted.qmd
Update tutorials/getstarted.qmd
Co-authored-by: Mateusz Baran <mateuszbaran89@gmail.com>

The term “exponential” has at least three different meanings throughout Lie groups and Riemannian manifolds.
To be precise, we call the just introduced one “exponential function”, since it often agrees with the [exponential](https://en.wikipedia.org/wiki/Exponential_function).

>>>>

The term “exponential” has at least three different meanings throughout Lie groups and Riemannian manifolds.
To be precise, we call the just introduced one “exponential function”, since it often agrees with the [matrix exponential](https://en.wikipedia.org/wiki/Matrix_exponential).
